Introduction

### 2015-07-20 dissertation/problems.tex
smaller things
evaluation problems small changes

\begin{problem}
How can the adoption of existing vocabularies be encouraged?
\end{problem}

@@

\begin{problem}
Evaluation methodologies has little foundation in philosophy of science.
\end{problem}

@@

However, a more interesting case is where an application (in a broad
sense) can adapt to the data it is seeing. For example, say that there
is an implementation of a Boat and a Car. It may not have been
anticipated when the application was first developed, but the
application sees an AmphibiousVehicle. Since it already knows how to
propel a Car and Boat, it should be able to adapt to the situation
given the context of whether the vehicle is on the road or in water.

>>>>

\begin{problem}
How can the adoption of existing vocabularies be encouraged? 
% TODO: Find the ref by Frank on the economics
\end{problem}

@@

Even if laws have been found that can make extrapolations across
orders of magnitude tenable, evaluations still pose significant
epistemological problems. For example, falsificationism, as argued by
Karl Popper and adopted in \cite{avinatguide} will be unsuited, for
reasons that more recent philosophers have pointed out, see
\cite{chalmers1999whatis} for a comprehensive discussion: If it is
insisted that hypotheses must be falsifiable, how can a researcher
know if their hypothesis should be rejected, or if it is something
wrong with the law, or perhaps the experiment itself?

\begin{problem}
Evaluation methodologies have little foundation in philosophy of science.
\end{problem}

@@

However, a more interesting case is where an application (in a broad
sense) can adapt to the data it is seeing. For example, say that there
is an implementation of a \rdfterm{Boat} and a \rdfterm{Car}. It may
not have been anticipated when the application was first developed,
but the application sees an \rdfterm{AmphibiousVehicle}. Since it
already knows how to propel a \rdfterm{Car} and \rdfterm{Boat}, it
should be able to adapt to the situation given the context of whether
the vehicle is on the road or in water.
